Parallelizing AdaBoost and Decision Trees

### 2015-08-01 paper.tex
paper changes

\section{Decision Trees}

\begin{thebibliography}
\ref[no1] Rob Schapire

>>>>

\section{Decision Trees}
Decision trees are a well-known method useful for classification which partitions the feature space into rectangular regions and gives each region the most common label among the training set points it contains. Each partition of the feature space is made along coordinate axes and done in a heirarchical way. Starting with the entire space, a line parallel to an axis divides it into two regions and then the same is done for these resulting regions. This process is repeated many times until the space is partitioned into several rectangles, like the example in Figure 1 (\cite{HTF}).
\begin{figure}
\includegraphic{dectreerect}
\end{figure}

 In that depiction, the lines drawn at $t_i$ represent the $i$th division of the space. Since each region is divided in two, this gives rise to a binary tree where each node represents a line drawn to partition the region existing before that node. The tree corresponding to Figure 1 is given in Figure 2 (\cite{HTF}).

 It is done in a heirarchical way that The feature space is partitioned along coordinate axes, which gives rise to decision. The most common way to partition the feature space is along coordinate axes.

%\maketitle
%
%\section{Introduction}
%Binary and multiclass classification is a fundamental problem in machine
%learning and is commonly one of the first concepts to be studied in an
%introductory course, the goal being to accurately predict the label of a given
%observations using the data associated with the observation. In the context of
%binary classification, a labeled observation (or sample point) is a coordinate
%pair $(x, y)$ where $x\in\mathbb{R}^d$ is a vector of data associated with the
%observation (feature vector) and $y\in\{1, -1\}$ is the corresponding label of
%the observation. This classification, and even prediction in general, commonly
%splits up into two different scenarios, supervised and unsupervised learning.
%Supervised learning involves taking a set of labeled observations (training
%set) and using it to construct a prediction function, one that can take a new
%feature vector and predict the corresponding label. There are many methods used
%for classification in supervised learning, including support vector machines,
%decision trees, online algorithms, and many others.
%
%A weak learning algorithm, or weak learner, is an algorithm that, given a set of training data, yields a predictor with performance of at least 50\% percent accuracy, or just better than random guessing. The prediction functions that a weak learner returns are called base classifiers. There was an important question asking whether the base classifiers from a weak learner could somehow be joined together to produce a strong learner, or an algorithm that gives a prediction function of arbitrary accuracy.
%
%Boosting is a category of methods that addresses this question, which Freund and Schapire
%successfully answered with their algorithm AdaBoost. AdaBoost, which stands for adaptive boosting, builds
%a more accurate predictor through successive rounds of training a weak learner
%to the data and subsequently re-weighting the training samples \cite{no1}.

\begin{thebibliography}
\ref[no1] Yoav Freund Rob Schapire

\ref[no2] Hastie Friedman Tibshirani

\ref[no3] Mohri

\ref[no4] Wiki
